---
title: "Source code for synthetic experiments in “Globally-Optimal Greedy Experiment Selection for Active Sequential Estimation”"
author: "Hongru Zhao"
date: "2023-11-04"
output: pdf_document
---
\section{Basic Functions}
```{r  }
# basic matrix function such as eye, ones, zeros, dot
library(pracma)
library(latex2exp)
library(glmnet)
library(dplyr)
### Kendall' tau
library(Kendall)
library(igraph)
library(parallel)
num_cores=7
#### solving optimal proportion
{
  ### projection functions
  project_to_simplex <- function(pi_0) {
    # Sort pi_0 in decreasing order
    sorted_pi <- sort(pi_0, decreasing = TRUE)
    # Compute cumulative sum
    cumsum_pi <- cumsum(sorted_pi)
    # Find the largest index rho
    rho<-max(which(sorted_pi*seq_along(sorted_pi)>(cumsum_pi - 1)))
    # Calculate lambda
    lambda <- (cumsum_pi[rho] - 1) / rho
    # Return the projection of pi_0 onto the simplex
    return(pmax(pi_0 - lambda, 0))
  }
  project_onto_box <- function(v, box=c(-5,5)) {
    return(pmin(pmax(v, box[1]), box[2]))
  }
  # using projected gradient descent to solve optimal proportion
  projected_gradient_descent <- function(pi_0_initial, num_iters=10000, learning_rate=0.01, grad_obj, tol = 1e-8) {
    pi_0 <- pi_0_initial
    for (i in 1:num_iters) {
      pi_0_old <- pi_0
      gradient <- grad_obj(pi_0)  # Compute the gradient
      pi_0 <- pi_0 - learning_rate * gradient  # Gradient step
      pi_0 <- project_to_simplex(pi_0)  # Projection step
      # Check for convergence
      if (max(abs(pi_0 - pi_0_old)) < tol) {
        break
      }
    }
    return(pi_0)
  }
  obj_inverse_full <- function(pi_0) {
    t0 <- design_X %*% theta + offset_b
    p0 <- exp(t0) / (1 + exp(t0))
    return_val <- matrix(rep(0,p^2), nrow = p, ncol = p)
    for (a in 1:k){
      term <- design_X[a,] %*% t(design_X[a,]) * pi_0[a] * p0[a] * (1 - p0[a])
      return_val <- return_val + term
    }
    return(solve(return_val))
  }
  obj_f_full <- function(pi_0) { 
    return(sum( diag( obj_inverse_full(pi_0) ) ))
  }
  # Gradient of the objective function
  grad_f_full <- function(pi_0) {
    t0 <- design_X %*% theta + offset_b
    p0 <- exp(t0) / (1 + exp(t0))
    # Embed the content of obj_inverse_full
    return_val <- matrix(rep(0,p^2), nrow = p, ncol = p)
    for (a in 1:k){
      term <- design_X[a,] %*% t(design_X[a,]) * pi_0[a] * p0[a] * (1 - p0[a])
      return_val <- return_val + term
    }
    I_pi = solve(return_val)
    # Continue with grad_f_full
    z <- numeric(k)
    for (a in 1:k){
      z[a] <- sum( (I_pi %*% design_X[a,])^2 )  * p0[a] * (1 - p0[a])
    }
    return(-z)
  }
}
### calculate I^{\pi}
I_pi_truncate <- function(design_X, p0, n_d, epsilon = 1e-11) {
  # Adjust p0 values based on epsilon
  p0[p0 < epsilon|p0 >1- epsilon] <- epsilon
  # Compute the weights
  w <- n_d * p0 * (1 - p0)
  # Scale the rows of design_X by the weights
  X_scaled <- design_X * w
  # Compute the matrix product
  result <- t(design_X) %*% X_scaled
  return(result)
}

# GI0/GI1 selection for computerized adaptive testing (CAT) for simulation study 1 in Section 7 
adapt_seq_tr_glmnet <- function( design_X, init_data,  method.order = 1 , n_max = 100 , pi_optimized, off_set=off_set ,n_rep) {
#  design_X represents the design matrix for all possible experiments
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  n_d=rep(n_rep,k)
  offset_b=dt_adp$OFFSET_b
  L2_Dis=rep(0,n-k0)
#  pi_loss=rep(0,n-k0)
  #  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    t0 <- -abs(as.numeric(design_X %*% theta_loop ) + off_set )
    #expit function
    p0 <- plogis(t0)
    return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
    if (method.order ==1)
    {
      inv_X=solve(return_val , t(design_X) ) 
      zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
    }else{
      for (a in 1:k){
        # Obtain the vector of fitted probabilities
        zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
      }
    }
    action=which.min(zero_first_order_index)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for two parameter logistic (2PL) model
    linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop) )
}

opt_seq_tr_glmnet <- function( design_X, init_data,  method.order = 1 , n_max = 100 , pi_optimized, off_set=off_set ,n_rep) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  n_d=rep(n_rep,k)
  offset_b=dt_adp$OFFSET_b
  L2_Dis=rep(0,n-k0)
#  pi_loss=rep(0,n-k0)
  #  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    t0 <- -abs(as.numeric(design_X %*% theta ) + off_set )
    #expit function
    p0 <- plogis(t0)
    return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
    if (method.order ==1)
    {
      inv_X=solve(return_val , t(design_X) ) 
      zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
    }else{
      for (a in 1:k){
        # Obtain the vector of fitted probabilities
        zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
      }
    }
    action=which.min(zero_first_order_index)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for two parameter logistic (2PL) model
    linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
    #    pi_loss[i-k0] = obj_f_full(n_d/i)
    #    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop) )
}

adapt_seq_tr_glmnet_stopping_time <- function( design_X, init_data,  method.order = 1 , n_max = 100000 , pi_optimized, off_set=off_set ,n_rep, stopping_d,stopping_c) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  n_d=rep(n_rep,k)
  offset_b=dt_adp$OFFSET_b
  L2_Dis=rep(0,n-k0)
  #  pi_loss=rep(0,n-k0)
  #  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,      
                           standardize=FALSE,
                           intercept=FALSE,
                           lower.limits=-3,upper.limits=3,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    t0 <- -abs(as.numeric(design_X %*% theta_loop ) + off_set )
    #expit function
    p0 <- plogis(t0)
    return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
    if(dot(solve(return_val,stopping_d) ,stopping_d)<stopping_c){break}
    if (method.order ==1)
    {
      inv_X=solve(return_val , t(design_X) ) 
      zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
    }else{
      for (a in 1:k){
        zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
      }
    }
    action=which.min(zero_first_order_index)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for two parameter logistic (2PL) model
    linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
    #    pi_loss[i-k0] = obj_f_full(n_d/i)
    #    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop) )
}

```
\section{Simulation study 1: computerized adaptive testing (CAT)}
\subsection{Task 1: Optimal Proportion}
```{r}
# initial data
node=seq(-1.5,1.5,0.1)
pi_matrix= matrix(0 ,nrow=length(node), ncol=3)
for(i in 1:length(node) ){
  {
    p=2
    k=3
    theta_1_fixed=1
    theta_2_nonfixed=node[i]
    # Generate the logistic regression coefficients
    theta <- c(theta_1_fixed,theta_2_nonfixed)
    samples <- matrix(c(1,0,1/2,0,1,1), ncol = p)
    offset_b=c(-0.1,0,0)
    # Create a data frame with the random samples
    dt1 <- as.data.frame( samples )
    # Generate the linear predictor for two parameter logistic (2PL) model
    linear_predictor <- samples %*% theta + offset_b
    {
      # Generate the probabilities using the logistic function
      probabilities <- 1 / (1 + exp(-linear_predictor))
    } 
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(k, size = 1, prob = probabilities)
    dt1$Y <- y0
    dt1$OFFSET_b <-offset_b
    dt_adp=dt1
    suppressWarnings({model <- glm(Y ~ .-1-OFFSET_b, data = dt1, family = binomial(link = "logit"),offset=OFFSET_b) })
    design_X <- model.matrix(model)  
  }
  pi_0_initial=rep(1/k,k)
  num_iter=10000
  learning_rate=0.001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial,num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full)
  pi_matrix[i,]=pi_optimized
}
```

\subsection{Optimal \(\pi^*\)  as a function of \(\theta_2\)}
Plot \( \pi^*\) as a function of \(\theta=(1,\theta_2),\theta_2\in[-1.5,1.5]\).  
```{r}
par(mar = c(4.2, 4.2, 1, 1))
par(mfrow = c(1, 1))
# Create a vector of labels for the legend
legend_labels <- c(expression(paste(pi, "*(1)")), expression(paste(pi, "*(2)")), expression(paste(pi, "*(3)")))

plot(node, pi_matrix[, 1],ylim = c(0, 0.75),  type = "l", col = 1, xlab = expression(theta[2]),ylab="Optimal Proportion")

for(i in 2:ncol(pi_matrix)) {
  lines(node, pi_matrix[, i], col = i)
}
# Add a legend to the plot
legend("topright", legend = legend_labels, col = 1:3, lty = 1, cex = 0.8,bty="n")
```

\subsection{Task 4: Histogram and CI}
Let  \(\theta=(1,0)\). Generate initial data.
```{r}
# Generate initial data for CAT
generate_data_cat <- function(n_rep){
  p=2
  k=3
  theta_1_fixed=1
  theta_2_nonfixed=0
  # Generate the logistic regression coefficients
  theta <- c(theta_1_fixed,theta_2_nonfixed)
  samples <- matrix(c(1,0,1/2,0,1,1), ncol = p)
  offset_b=c(-0.1,0,0)
  for(jjj in 1:n_rep){
  dt1 <- as.data.frame( samples )
  # Generate the linear predictor for two parameter logistic (2PL) model
  linear_predictor <- samples %*% theta + offset_b
  {
  # Generate the probabilities using the logistic function
    probabilities <- 1 / (1 + exp(-linear_predictor))
  } 
  # Generate the response variable Y based on the probabilities
  y0 <- rbinom(k, size = 1, prob = probabilities)
  dt1$Y <- y0
  dt1$OFFSET_b <-offset_b
  if(jjj==1){dt_adp=dt1}else{dt_adp=rbind(dt_adp,dt1)}
  }
  # Obtain design matrix design_X
  suppressWarnings({model <- glm(Y ~ .-1-OFFSET_b, data = dt1, family = binomial(link = "logit"),offset=OFFSET_b) })
  design_X <- model.matrix(model)  
  return(list(theta=theta, design_X=design_X, offset_b=offset_b, dt1=dt_adp ))
}

p=2
k=3
n_rep=3
ddaattaa=generate_data_cat(n_rep)
theta=ddaattaa$theta
design_X=ddaattaa$design_X
offset_b=ddaattaa$offset_b
dt1=ddaattaa$dt1

init_data=dt1
  set.seed(123456)
  l_max=1000
  k0 = nrow(dt1)
  n_max = 50
  pi_optimized=pi_matrix[16,]
```

Plot of Histogram vs standard normal Density  
```{r}
generate_plot_data <- function(design_X, init_data, theta, offset_b, repeat_n=50, n_max=50, opt_pi, method.order=1) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0=nrow(init_data)
  ### set initial data
  theta_matrix = matrix(0, ncol = p, nrow = repeat_n)
  for(j in 1:repeat_n){
    output0=adapt_seq_tr_glmnet(design_X, init_data, 
                                method.order=method.order,
                                n_max=n_max, 
                                pi_optimized=pi_optimized,
                                off_set=offset_b,
                                n_rep)
    dt_adp=output0$final_data
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    theta_matrix[j,] = theta_loop-theta
  }    
  theta_vec=theta_loop-theta
  return(list(  theta_matrix=theta_matrix,
                theta_vec=theta_vec))
}
n_m=50
l_mmax=1000
output0=generate_plot_data(design_X=design_X,  init_data=init_data, theta=theta, offset_b=offset_b,  repeat_n=l_mmax, n_max=n_m, opt_pi=pi_optimized, method.order=0)
theta_matrix=output0$theta_matrix
{
par(mfrow = c(1, 2))
rand_vec = c(1, 0)
t_vec=theta_matrix%*%rand_vec * sqrt(n_m) /as.numeric(sqrt(rand_vec %*% obj_inverse_full(pi_optimized)%*% rand_vec))
# Define the x values
x <- seq(min(t_vec), max(t_vec), by = 0.01)
# Calculate the y values using dnorm
y <- dnorm(x, sd=1)
# Create a histogram
hist(t_vec,breaks=15 , probability = TRUE,   main = "Histogram for GI0",xlab="")
# Add the normal distribution line
lines(x, y, col = "blue")

rand_vec = c(0, 1)
t_vec=theta_matrix%*%rand_vec * sqrt(n_m)/as.numeric(sqrt(rand_vec %*% obj_inverse_full(pi_optimized)%*% rand_vec))
# Define the x values
x <- seq(min(t_vec), max(t_vec), by = 0.01)
# Calculate the y values using dnorm
y <- dnorm(x)

# Create a histogram
hist(t_vec,breaks=15 , probability = TRUE,   main = "Histogram for GI0" ,xlab="")
# Add the normal distribution line
lines(x, y, col = "blue")

# Reset to default single plot layout
par(mfrow = c(1, 1))
}

output1=generate_plot_data(design_X=design_X,  init_data=init_data, theta=theta, offset_b=offset_b,  repeat_n=l_mmax, n_max=n_m, opt_pi=pi_optimized, method.order=1)
theta_matrix=output1$theta_matrix

{
par(mfrow = c(1, 2))
## Create the first plot (this will go on the left)
rand_vec = c(1, 0)
t_vec=theta_matrix%*%rand_vec * sqrt(n_m) /as.numeric(sqrt(rand_vec %*% obj_inverse_full(pi_optimized)%*% rand_vec))
# Define the x values
x <- seq(min(t_vec), max(t_vec), by = 0.01)
# Calculate the y values using dnorm
y <- dnorm(x, sd=1 )
# Create a histogram
hist(t_vec,breaks=15 , probability = TRUE,   main = "Histogram for GI1",xlab="")
# Add the normal distribution line
lines(x, y, col = "blue")

## Create the second plot (this will go on the right)
rand_vec = c(0, 1)
# Generate some random data
t_vec=theta_matrix%*%rand_vec * sqrt(n_m)/as.numeric(sqrt(rand_vec %*% obj_inverse_full(pi_optimized)%*% rand_vec))
# Define the x values
x <- seq(min(t_vec), max(t_vec), by = 0.01)
# Calculate the y values using dnorm
y <- dnorm(x)

# Create a histogram
hist(t_vec,breaks=15 , probability = TRUE,   main = "Histogram for GI1" ,xlab="")
# Add the normal distribution line
lines(x, y, col = "blue")
# Reset to default single plot layout
par(mfrow = c(1, 1))
}
```

Coverage probability for CI 
```{r}
p=2
k=3
n_rep=3
set.seed(345)
ddaattaa=generate_data_cat(n_rep)
theta=ddaattaa$theta
design_X=ddaattaa$design_X
offset_b=ddaattaa$offset_b
dt1=ddaattaa$dt1

init_data=dt1
k0=nrow(dt1)
pi_optimized=pi_matrix[16,]

l_max=1000
z_score=qnorm(1-0.05/2)
stopping_d=rnorm(2)
stopping_d=stopping_d/norm(stopping_d,"2")
  
counting_non_random=rep(0,6) 
dim(counting_non_random)=c(2,3)
n_care=c(25,50,100)
for(m.order in c(0,1)){
for(ijk in 1:3){
for(ij in 1:l_max){
  n_max=n_care[ijk]
  output_CI=adapt_seq_tr_glmnet( design_X, init_data, method.order = m.order , n_max = n_max , pi_optimized, off_set=offset_b ,n_rep)
  t0 <- -abs(as.numeric(design_X %*% output_CI$final_beta ) + offset_b )
    #expit function
  p0 <- plogis(t0)
  return_val=I_pi_truncate(design_X, p0, output_CI$n_d, epsilon = 0)
  if(
    abs(dot(stopping_d,output_CI$final_beta-theta)) <
    z_score*sqrt(dot(solve(return_val, stopping_d),stopping_d) ) ){counting_non_random[m.order+1,ijk]=counting_non_random[m.order+1,ijk]+1}
    }
  }
}
```

Coverage probability for stopping time CI 
```{r}
counting_random=rep(0,2)  
dim(counting_random)=c(2,1)
c_care=0.1

t11=Sys.time()
for(method.order in c(0,1)){
  for(ijk in 1){
    for(ij in 1:l_max){
  n_max=n_care[ijk]
  stopping_d=rnorm(2)
  stopping_d=stopping_d/norm(stopping_d,"2")
  stopping_c=c_care[ijk]
  output_CI=adapt_seq_tr_glmnet_stopping_time( design_X, init_data, method.order = method.order , n_max = 100000 , pi_optimized, off_set=offset_b ,n_rep, stopping_d,stopping_c^2)
  if(
    abs(dot(stopping_d,output_CI$final_beta-theta))<z_score*stopping_c
    ){counting_random[method.order+1,ijk]=counting_random[method.order+1,ijk]+1}
    }
  }
}  
t22=Sys.time()
print(t22-t11)
counting_random
```

\subsection{Task 2: Plot of empirical \(\overline{\pi}_n \) vs optimal \(\pi^*\)}
```{r}
n_max = 50
# Empirical Proportions
method.order = 0
  {
    set.seed(123)
    pi_optimized=pi_matrix[16,]
    k = nrow( design_X )
    p = ncol( design_X )
    k0=nrow(init_data)
    n = n_max
    dt_adp=init_data 
    n_d=rep(n_rep,k)

    n_d_matrix_Gi=matrix(0,nrow=n-k0, ncol=k)
    L2_Dis_Gi=rep(0,n-k0)
    j=0
    for (i in (k0+1):n){
      zero_first_order_index=rep(0,k)
      suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
      })
      theta_loop=as.numeric(model_loop$beta)
      L2_Dis_Gi[i-k0]=sum( (theta_loop - theta)^2  )
      t0 <- design_X %*% theta_loop + offset_b
      p0 <- as.numeric(1 / (1 + exp(-t0)) )
      return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
      if (method.order ==1)
      {
        iinnvv=solve(return_val)
        for (a in 1:k){
          zero_first_order_index[a]=-sum((iinnvv%*%design_X[a,])^2)*p0[a]*(1-p0[a])
        }    
      }
      else
      {
        for (a in 1:k){
          # Obtain the vector of fitted probabilities
          zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
        } 
      }
      action=which.min(zero_first_order_index)
      n_d[action]=n_d[action]+1
      # Generate the new linear predictor for two parameter logistic (2PL) model
      linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
      # Generate the probabilities using the logistic function
      probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
      # Generate the response variable Y based on the probabilities
      y0 <- rbinom(1, size = 1, prob = probabilities)
      dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
      n_d_matrix_Gi[i-k0,]=n_d/sum(n_d)
    }
  }
   ### Plot of empirical proportion for GI0
  { 
    par(mfrow = c(1, 2))
    node2=(k0+1):n
    # Create a vector of labels for the legend
    legend_labels <- c(expression(paste("Emperical ",pi[n] ,"(1)     ")), expression(paste("Emperical ",pi[n] ,"(2)")), expression(paste("Emperical ",pi[n] ,"(3)")),
                       expression(paste(pi ,"*(1)")), expression(paste(pi ,"*(2)")), expression(paste(pi ,"*(3)")) )
    # Set up the plot with the first column of the matrix
    plot(node2 , n_d_matrix_Gi[ , 1],ylim = c(0, 0.75), type = "p", col = 1, xlab = "Sample Size",ylab="",pch = 20,cex.lab=1.5)
    abline(h = pi_optimized[1],lty = 2)
    # Use a loop to add each subsequent column to the plot as a new line
    for(i in 2:ncol(pi_matrix)) {
      points(node2 , n_d_matrix_Gi[ , i], col = i, lty=2, pch = 20)
      abline(h = pi_optimized[i],  col = i,lty = 2)
    }
    # Add a legend to the plot
    legend("topright", legend = legend_labels, col = c(1:3, 1:3), pch = c(20, 20, 20, NA, NA, NA), lty = c(NA, NA, NA, 2, 2, 2), ncol=2,bty="n")
    title(main = "Empirical Proportion for GI0")
      }

method.order = 1
  {
  ### GI method
  {
    set.seed(123)
    pi_optimized=pi_matrix[16,]
    k = nrow( design_X )
    p = ncol( design_X )
    k0=nrow(init_data)
    n = n_max
    dt_adp=init_data 
    n_d=rep(n_rep,k)

    n_d_matrix_Gi=matrix(0,nrow=n-k0, ncol=k)
    L2_Dis_Gi=rep(0,n-k0)
    Kendall_rank_Gi=rep(0,n-k0)
    theta_loop_init=rep(0,p)
    j=0
    for (i in (k0+1):n){
      zero_first_order_index=rep(0,k)
      suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
      })
      theta_loop=as.numeric(model_loop$beta)
      L2_Dis_Gi[i-k0]=sum( (theta_loop - theta)^2  )
      t0 <- design_X %*% theta_loop + offset_b
      p0 <- as.numeric(1 / (1 + exp(-t0)) )
      return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
      if (method.order ==1)
      {   
        iinnvv=solve(return_val)
        for (a in 1:k){
          # Obtain the vector of fitted probabilities
          t0=exp(dot(theta_loop,design_X[a,])  +offset_b[a])
          p_0=t0/(1+t0)
          zero_first_order_index[a]=-sum((iinnvv%*%design_X[a,])^2)*p_0*(1-p_0)
        }    
      }
      else
      {
        for (a in 1:k){
          # Obtain the vector of fitted probabilities
          zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
        } 
      }
      action=which.min(zero_first_order_index)
      n_d[action]=n_d[action]+1
      # Generate the new linear predictor for two parameter logistic (2PL) model
      linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
      # Generate the probabilities using the logistic function
      probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
      # Generate the response variable Y based on the probabilities
      y0 <- rbinom(1, size = 1, prob = probabilities)
      dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
      n_d_matrix_Gi[i-k0,]=n_d/sum(n_d)
    }
  }
}
  ### Plot of empirical proportion for GI1
  {
    node2=(k0+1):n
    # Create a vector of labels for the legend
    legend_labels <- c(expression(paste("Emperical ",pi[n] ,"(1)     ")), expression(paste("Emperical ",pi[n] ,"(2)")), expression(paste("Emperical ",pi[n] ,"(3)")),
                       expression(paste(pi ,"*(1)")), expression(paste(pi ,"*(2)")), expression(paste(pi ,"*(3)")) )
    #legend_labels=NULL
    # Set up the plot with the first column of the matrix
    plot(node2 , n_d_matrix_Gi[ , 1] ,ylim = c(0, 0.75), type = "p", col = 1, xlab = "Sample Size",ylab="",pch = 20,cex.lab=1.5)
    abline(h = pi_optimized[1],lty = 2)
    
    # Use a loop to add each subsequent column to the plot as a new line
    for(i in 2:ncol(pi_matrix)) {
      points(node2 , n_d_matrix_Gi[ , i], col = i, lty=2, pch = 20)
      abline(h = pi_optimized[i],  col = i,lty = 2)
      
    }
    
    # Add a legend to the plot
    legend("topright", legend = legend_labels, col = c(1:3, 1:3), pch = c(20, 20, 20, NA, NA, NA), lty = c(NA, NA, NA, 2, 2, 2),ncol=2,bty="n")
    title(main = "Empirical Proportion for GI1")
  }
par(mfrow = c(1, 1))

```

\subsection{Task 3: GI0/GI1/uniform/opt non-random select/opt random selection distance}
```{r}
p=2
k=3
n_rep=3
set.seed(334455)

ddaattaa=generate_data_cat(n_rep)
theta=ddaattaa$theta
design_X=ddaattaa$design_X
offset_b=ddaattaa$offset_b
dt1=ddaattaa$dt1

init_data=dt1
k0=nrow(init_data)
pi_optimized=pi_matrix[16,]

n_max=50
l_max=20000
#GI0/GI1/uniform/opt non-random select/opt random
  L2_Dis_Gi0_ave=rep(0,n_max-k0)
  L2_Dis_Gi1_ave=rep(0,n_max-k0)
  L2_Dis_Gi0opt_ave=rep(0,n_max-k0)
  L2_Dis_Gi1opt_ave=rep(0,n_max-k0)
  L2_Dis_unif_ave=rep(0,n_max-k0)
  L2_Dis_opt_D=rep(0,n_max-k0)
  L2_Dis_opt_R=rep(0,n_max-k0)
  
  L2_Dis_unif=rep(0,n_max-k0)
  L2_Dis_opt_ave_D=rep(0,n_max-k0)
  L2_Dis_opt_ave_R=rep(0,n_max-k0)
for(l in 1:l_max){
p=2
k=3
n_rep=3

  method.order = 0
  ### GI0 method
  output_GI0=adapt_seq_tr_glmnet( design_X, init_data, 
                                  method.order = method.order,
                                  n_max = n_max ,
                                  pi_optimized, 
                                  off_set=offset_b,
                                  n_rep) 
  L2_Dis_Gi0_ave=L2_Dis_Gi0_ave+output_GI0$L2_Dis
  
  method.order = 1
  ### GI1 method
  output_GI1=adapt_seq_tr_glmnet( design_X, init_data, 
                                  method.order = method.order,
                                  n_max = n_max ,
                                  pi_optimized,
                                  off_set=offset_b ,n_rep) 
  L2_Dis_Gi1_ave=L2_Dis_Gi1_ave+output_GI1$L2_Dis
  
  method.order = 0
  ### GI0 opt
  output_GI0_opt=  opt_seq_tr_glmnet( design_X, init_data,
                                  method.order = method.order,
                                  n_max = n_max ,
                                  pi_optimized,
                                  off_set=offset_b,
                                  n_rep) 
  L2_Dis_Gi0opt_ave=L2_Dis_Gi0opt_ave+output_GI0_opt$L2_Dis
  
  method.order = 1
  ### GI1 opt
  output_GI1_opt=opt_seq_tr_glmnet( design_X, init_data, 
                                  method.order = method.order,
                                  n_max = n_max ,
                                  pi_optimized,
                                  off_set=offset_b,
                                  n_rep)
  L2_Dis_Gi1opt_ave=L2_Dis_Gi1opt_ave+output_GI1_opt$L2_Dis
  
  ### uniform
  {
    dt_adp_unif=init_data 
    n_d_unif=rep(n_rep,k)
    for (i in (k0+1):n_max){
      suppressWarnings({ 
      model_loop <- glmnet(dt_adp_unif[,c(1,2)],
                           dt_adp_unif$Y,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp_unif$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,
                           lambda=0)
      })
      theta_loop=as.numeric(model_loop$beta)
      L2_Dis_unif[i-k0]=sum( (theta_loop - theta)^2  )
      L2_Dis_unif_ave[i-k0]=L2_Dis_unif_ave[i-k0]+L2_Dis_unif[i-k0]
      action=sample(1:k,1)
      n_d_unif[action]=n_d_unif[action]+1
      # Generate the new linear predictor for two parameter logistic (2PL) model
      linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
      # Generate the probabilities using the logistic function
      probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
      # Generate the response variable Y based on the probabilities
      y0 <- rbinom(1, size = 1, prob = probabilities)
      dt_adp_unif=as.data.frame(rbind(dt_adp_unif,c(design_X[action,],y0,offset_b[action])) )
#      n_d_matrix_unif[i-k0,]=n_d_unif/sum(n_d_unif)
    }
  }
  ### opt non-random
  {
    dt_adp=init_data 
    n_d=rep(n_rep,k)
    for (i in (k0+1):n_max){
      zero_first_order_index=rep(0,k)
            suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
      })
      theta_loop=as.numeric(model_loop$beta)
      L2_Dis_opt_D[i-k0]=sum( (theta_loop - theta)^2  )
      L2_Dis_opt_ave_D[i-k0]=L2_Dis_opt_ave_D[i-k0]+L2_Dis_opt_D[i-k0]
      ### nonrandom
      action = which.min( n_d/sum(n_d) - pi_optimized)
      n_d[action]=n_d[action]+1
      # Generate the new linear predictor for two parameter logistic (2PL) model
      linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
      # Generate the probabilities using the logistic function
      probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
      # Generate the response variable Y based on the probabilities
      y0 <- rbinom(1, size = 1, prob = probabilities)
      dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
    }
  }
  ### opt random select
  {
    dt_adp=init_data 
    n_d=rep(n_rep,k)
    for (i in (k0+1):n_max){
      zero_first_order_index=rep(0,k)
            suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,c(1,2)], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           offset=dt_adp$OFFSET_b,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-3,upper.limits=3,lambda=0)
      })
      theta_loop=as.numeric(model_loop$beta)
      L2_Dis_opt_R[i-k0]=sum( (theta_loop - theta)^2  )
      L2_Dis_opt_ave_R[i-k0]=L2_Dis_opt_ave_R[i-k0]+L2_Dis_opt_R[i-k0]
      ### random
      action=sample(1:k,1,prob=pi_optimized)
      n_d[action]=n_d[action]+1
      # Generate the new linear predictor for two parameter logistic (2PL) model
      linear_predictor <- dot(design_X[action,],theta)+offset_b[action]
      # Generate the probabilities using the logistic function
      probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
      # Generate the response variable Y based on the probabilities
      y0 <- rbinom(1, size = 1, prob = probabilities)
      dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0,offset_b[action])) )
    }
  }
}
```

```{r}
par(mar = c(4.2, 4.2, 1, 1))
{
  node2=(k0+1):n_max
  # Create a vector of labels for the legend
  #legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random","Opt_GI0","Opt_GI1")
  legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random")
  plot(node2, L2_Dis_Gi0_ave/l_max ,ylim = c(0, 1.1*max(L2_Dis_Gi0_ave/l_max)), 
       type = "o",  xlab = "Sample Size",ylab="MSE",
       cex=0.8, col = "grey30", lwd = 1, pch=21,cex.lab=1.5)
  lines(node2, L2_Dis_Gi1_ave/l_max, type = "o",
        cex=0.5, col = "green",lwd = 1, lty=2, pch=19)
  lines(node2, L2_Dis_unif_ave/l_max, type = "o",
        cex=0.7, col = 4,lwd = 1, lty=4, pch=24)
  lines(node2, L2_Dis_opt_ave_D/l_max, type = "o",
        cex=0.5,  col = "red",lwd = 1, lty=3, pch=3)
  lines(node2, L2_Dis_opt_ave_R/l_max, type = "o",
        cex=0.7,  col = 6, lty=5, pch=7)
#  lines(node2 , L2_Dis_Gi0opt , col = 3)
#  lines(node2 , L2_Dis_Gi1opt , col = 7,lty=4)
  # Add a legend to the plot
  legend("topright", legend = legend_labels, 
         col = c("grey30", "green", 4, "red", 6), 
         lwd = c(1, 1, 1, 1, 1),
         lty = c(1, 2, 4, 3, 5), 
         cex = 1,
         pch = c(21,19, 24,3, 7), 
         bty="n")

}
```

\section{Simulation study 2: Rank Aggregation}
```{r}
# generate ranking data
data_random_generator <- function(p_plus, connected_pair_matrix){
  p=p_plus-1
  k=nrow(connected_pair_matrix)
  # Generate the logistic regression coefficients
  theta <- runif(p ,min = -2, max = 2)
  design_matrix <-  matrix(0, nrow = k, ncol = p_plus)
  for (row in 1:k ) {
    design_matrix[row, as.numeric(connected_pair_matrix[ row,2]) ]  <- -1
    design_matrix[row, as.numeric(connected_pair_matrix[ row,1]) ]  <-  1
  }
  samples=design_matrix[,-1]
  # Create a data frame with the random samples
  dt1 <- as.data.frame( samples )
  # Generate the linear predictor  
  linear_predictor <- samples %*% theta  
  # Generate the probabilities using the logistic function
  probabilities <- 1 / (1 + exp(-linear_predictor))
  # Generate the response variable Y based on the probabilities
  y0 <- rbinom(k, size = 1, prob = probabilities)
  dt1$Y <- y0
  dt_adp=dt1
  return( list(data_random = dt_adp, theta=theta)  )
}

init_edge_generate_RA <- function(p_plus, n_init, method = c("full", "min", "regular"), reg=4) {
  # Choose the method based on the input
  selected_method <- match.arg(method)
  p = p_plus-1
  # Implement different behaviors based on the selected_method
  if (selected_method == "regular") {
    ### Create a random regular graph
    regu_graph=sample_k_regular(p_plus, reg, directed = FALSE, multiple=FALSE)
    edge_regu_graph=as_edgelist(regu_graph)
    pair_matrix = edge_regu_graph
  }else{
    ### generate full Erdos-Renyi model
    full_graph=sample_gnm(p_plus, p_plus*(p_plus-1)/2)
    edge_full_graph=as_edgelist(full_graph)
  }
  if (selected_method == "full") {
    pair_matrix = edge_full_graph
  } else if (selected_method == "min") {
    ### Samples from the spanning trees of graph full_graph randomly and uniformly
    min_tree_pre=sample_spanning_tree(full_graph)
    min_tree <- subgraph.edges(full_graph, min_tree_pre)
    edge_min_tree=as_edgelist(min_tree)
    pair_matrix = edge_min_tree
  }
  k_seq = nrow(pair_matrix)
  # define design matrix
  design_matrix <-  matrix(0, nrow = k_seq, ncol = p_plus)
  for (row in 1:k_seq ) {
    design_matrix[row, as.numeric(pair_matrix[ row,2]) ]  <-  -1
    design_matrix[row, as.numeric(pair_matrix[ row,1]) ]  <-   1
  }
  design_X=design_matrix[,-1]
  ### Samples from the spanning trees of graph full_graph randomly and uniformly
  gra = make_graph(t(pair_matrix),directed=FALSE)
  min_tree_pre_init  = sample_spanning_tree(gra)
  min_tree_init <- subgraph.edges(gra, min_tree_pre_init)
  edge_min_tree_init = as_edgelist(min_tree_init)
  sample_pair_matrix=rbind(edge_min_tree_init,
              pair_matrix[sample(k_seq,n_init - p, replace = T),])

  ddt=data_random_generator(p_plus,sample_pair_matrix)
  theta=ddt$theta
  init_data=ddt$data_random
  
  sample_pair_matrix.df=as.data.frame(sample_pair_matrix)
  sample_pair_matrix.df$Y=init_data$Y
  # Aggregating the data
  suppressWarnings({
  aggregated_data <- sample_pair_matrix.df %>%
    group_by(V1, V2) %>%
    summarise(
      count_A_won_TRUE  = sum(Y,   na.rm = TRUE),
      count_A_won_FALSE = sum(!Y,  na.rm = TRUE),
      .groups = "drop" # This drops the grouping
    )
  })
  n_d_init=rep(0,k_seq)
  for (i in 1:k_seq){
    row=which(aggregated_data$V1==pair_matrix[i,1]&aggregated_data$V2==pair_matrix[i,2])
    #row=sample(row,1)
    vc=aggregated_data$count_A_won_TRUE+aggregated_data$count_A_won_FALSE
    if( length(vc[row]) == 1 ){n_d_init[i]=vc[row]}
  }
  return(list(pair_matrix=pair_matrix, design_X=design_X, 
              n_d_init=n_d_init, init_data=init_data, theta=theta ))
}

# GI0/GI1 selection for Rank Aggregation (RA) for simulation study 2 in Section 7 
adapt_seq_tr_glmnet_RA <- function( design_X, init_data,  method.order = 1 , n_max = 100 , pi_optimized, n_d, box_R=3) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  L2_Dis=rep(0,n-k0)
  pi_loss=rep(0,n-k0)
  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,1:p], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-box_R,
                           upper.limits=box_R,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    t0 <- -abs(as.numeric(design_X %*% theta_loop )    )
    #expit function
    p0 <- plogis(t0)
    return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
    if (method.order ==1)
    {
      inv_X=solve(return_val , t(design_X) ) 
      zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
    }else{
      for (a in 1:k){
        # Obtain the vector of fitted probabilities
        zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
      }
    }
    action=which.min(zero_first_order_index)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for BT model
    linear_predictor <- dot(design_X[action,],theta)
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0 ) ) )
    pi_loss[i-k0] = obj_f_full(n_d/i)
    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop, pi_loss=pi_loss, pi_L2_Dis=pi_L2_Dis) )
}
adapt_unif_glmnet_RA <- function( design_X, init_data,  n_max = 100 , pi_optimized, n_d, box_R=3) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  L2_Dis=rep(0,n-k0)
  pi_loss=rep(0,n-k0)
  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,1:p], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-box_R,
                           upper.limits=box_R,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    action=sample(1:k,1)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for BT model
    linear_predictor <- dot(design_X[action,],theta)
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0 ) ) )
    pi_loss[i-k0] = obj_f_full(n_d/i)
    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop, pi_loss=pi_loss, pi_L2_Dis=pi_L2_Dis) )
}
adapt_opt_D_glmnet_RA <- function( design_X, init_data,  n_max = 100 , pi_optimized, n_d, box_R=3) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  L2_Dis=rep(0,n-k0)
  pi_loss=rep(0,n-k0)
  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,1:p], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-box_R,
                           upper.limits=box_R,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    action = which.min( n_d/sum(n_d) - pi_optimized)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for BT model
    linear_predictor <- dot(design_X[action,],theta)
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0 ) ) )
    pi_loss[i-k0] = obj_f_full(n_d/i)
    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop, pi_loss=pi_loss, pi_L2_Dis=pi_L2_Dis) )
}
adapt_opt_R_glmnet_RA <- function( design_X, init_data,  n_max = 100 , pi_optimized, n_d, box_R=3) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  L2_Dis=rep(0,n-k0)
  pi_loss=rep(0,n-k0)
  pi_L2_Dis=rep(0,n-k0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,1:p], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-box_R,
                           upper.limits=box_R,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    action=sample(1:k,1,prob=pi_optimized)
#    action = which.min( n_d/sum(n_d) - pi_optimized)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for BT model
    linear_predictor <- dot(design_X[action,],theta)
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0 ) ) )
    pi_loss[i-k0] = obj_f_full(n_d/i)
    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop, pi_loss=pi_loss, pi_L2_Dis=pi_L2_Dis) )
}
oracle_seq_tr_glmnet_RA <- function( design_X, init_data,  method.order = 1 , n_max = 100 , pi_optimized, n_d, box_R=3) {
  k = nrow( design_X )
  p = ncol( design_X )
  k0 = nrow(init_data)
  n = n_max
  dt_adp=init_data 
  L2_Dis=rep(0,n-k0)
  pi_loss=rep(0,n-k0)
  pi_L2_Dis=rep(0,n-k0)
  t0 <- -abs(as.numeric(design_X %*% theta ))
  #expit function
  p0 <- plogis(t0)
  for (i in (k0+1):n){
    zero_first_order_index=rep(0,k)
    suppressWarnings({ 
      model_loop <- glmnet(dt_adp[,1:p], dt_adp$Y ,  
                           family = "binomial", alpha = 0,
                           standardize=FALSE,intercept=FALSE,
                           lower.limits=-box_R,
                           upper.limits=box_R,
                           lambda=0)
    })
    theta_loop=as.numeric(model_loop$beta)
    L2_Dis[i-k0]=sum( (theta_loop - theta)^2  )
    return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
    if (method.order ==1)
    {
      inv_X=solve(return_val , t(design_X) ) 
      zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
    }else{
      for (a in 1:k){
        # Obtain the vector of fitted probabilities
        zero_first_order_index[a]= sum(diag(solve(return_val+design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
      }
    }
    action=which.min(zero_first_order_index)
    n_d[action]=n_d[action]+1
    # Generate the new linear predictor for BT model
    linear_predictor <- dot(design_X[action,],theta)
    # Generate the probabilities using the logistic function
    probabilities <- exp(linear_predictor) / (1 + exp(linear_predictor))
    # Generate the response variable Y based on the probabilities
    y0 <- rbinom(1, size = 1, prob = probabilities)
    dt_adp=as.data.frame(rbind(dt_adp,c(design_X[action,],y0 ) ) )
    pi_loss[i-k0] = obj_f_full(n_d/i)
    pi_L2_Dis[i-k0] = sum( (pi_optimized-n_d/i)^2 )
  }
  return(list(n_d=n_d, L2_Dis=L2_Dis, final_data=dt_adp, final_beta=theta_loop, pi_loss=pi_loss, pi_L2_Dis=pi_L2_Dis) )
}

```

\subsection{Task 1: Calculation time }
```{r}
l_max=100
col_ind=0
cal_time = matrix(0,nrow=3,ncol=12)
for(p in c(25, 50, 100,500) ){
  # p_plus = p+1 number of objects
  p_plus = p + 1
  n_init=4*p
  n_max=n_init+1
  #
  for(word in c( "min", "regular" ,"full")){
    {
  otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method=word)
  n_d_init=otput$n_d_init
  theta=otput$theta
  init_data=otput$init_data
  design_X=otput$design_X
    }
  col_ind=col_ind+1
  for(kk in 1:l_max){
  ### GI1
  {
    method.order = 1
    {
      k = nrow( design_X )
      k0 = n_init
      n = n_max
      dt_adp=init_data 
      n_d=n_d_init
      ttttt_1=Sys.time() 
      {
        for (i in (k0+1):n){
          zero_first_order_index=rep(0,k)
          suppressWarnings({
            model_loop <- glmnet(dt_adp[,-(p+1)],dt_adp$Y,  
              family = "binomial", alpha = 0, 
              standardize=FALSE,intercept=FALSE,
              lower.limits=-3,upper.limits=3,lambda=0)
            })
          theta_loop=as.numeric(model_loop$beta)
          t0 <- -abs(as.numeric(design_X %*% theta_loop ) )
          #expit function
          p0 <- plogis(t0)
          return_val=I_pi_truncate(design_X, p0, n_d, epsilon = 0)
          {
            inv_X=solve(return_val , t(design_X) ) 
            zero_first_order_index= -colSums(inv_X^2)*p0*(1-p0)
          }
          action=which.min( zero_first_order_index )
          n_d[action]=n_d[action] +1
          Y=rbinom(1,1,plogis(dot(design_X[action,],theta)))
          # Generate the response variable Y based on the probabilities
          dt_adp = rbind(dt_adp,c(design_X[action,],Y) )
        }
      }
      ttttt_2=Sys.time() 
      cal_time[1,col_ind]=difftime(ttttt_2, ttttt_1, units = c("secs")) +cal_time[1,col_ind]
    }
  }
  ### GI0 par
  {
    method.order = 0
    {
      k = nrow( design_X )
      k0 = n_init
      n = n_max
      dt_adp=init_data 
      n_d=n_d_init
      cls <- makeCluster(num_cores)
      ttttt_1=Sys.time() 
      { 
        for (i in (k0+1):n){
          zero_first_order_index=rep(0,k)
          model_loop <- glmnet(dt_adp[,-(p+1)],
                               dt_adp$Y,  
                               family = "binomial", alpha = 0, 
                               standardize=FALSE,intercept=FALSE,
                               lower.limits=-3,upper.limits=3,lambda=0)
          theta_loop=as.numeric(model_loop$beta)
          # Obtain the vector of fitted probabilities
          t0 <- -abs(as.numeric(design_X %*% theta_loop ) )
          #expit function
          p0 <- plogis(t0)
          return_val= I_pi_truncate(design_X, p0, n_d, epsilon = 0) 
          {
            clusterExport(cls,c('return_val','p0','design_X'))
            zero_first_order_index=parSapply(cls, 1:k, function(a) {
              return(
                sum(diag(solve(return_val +design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))  ))
              )
            })
          }
          action=which.min( zero_first_order_index )
          n_d[action]=n_d[action] +1
          Y=rbinom(1,1,plogis(dot(design_X[action,],theta)))
          # Generate the response variable Y based on the probabilities
          dt_adp = rbind(dt_adp,c(design_X[action,],Y) )
        }
      }
      ttttt_2=Sys.time() 
      stopCluster(cls)
      cal_time[2,col_ind]=difftime(ttttt_2, ttttt_1, units = c("secs")) +cal_time[2,col_ind]
    }
  }
  ### GI0 un-par
  {
    method.order = 0
    {
      k = nrow( design_X )
      k0 = n_init
      n = n_max
      dt_adp=init_data 
      n_d=n_d_init
      ttttt_1=Sys.time() 
      { 
        for (i in (k0+1):n){
          zero_first_order_index=rep(0,k)
          model_loop <- glmnet(dt_adp[,-(p+1)],
                               dt_adp$Y,  
                               family = "binomial", alpha = 0, 
                               standardize=FALSE,intercept=FALSE,
                               lower.limits=-3,upper.limits=3,lambda=0)
          theta_loop=as.numeric(model_loop$beta)
          # Obtain the vector of fitted probabilities
          t0 <- -abs(as.numeric(design_X %*% theta_loop ) )
          #expit function
          p0 <- plogis(t0)
          return_val= I_pi_truncate(design_X, p0, n_d, epsilon = 0) 
          for(a in 1:k) {
            zero_first_order_index[a] <- sum(diag(
              solve( return_val  + design_X[a,] %*% t(design_X[a,]) * p0[a] * (1 - p0[a]))))
          }
          action=which.min( zero_first_order_index )
          n_d[action]=n_d[action] +1
          Y=rbinom(1,1,plogis(dot(design_X[action,],theta)))
          # Generate the response variable Y based on the probabilities
          dt_adp = rbind(dt_adp,c(design_X[action,],Y) )
        }
      }
      ttttt_2=Sys.time() 
      cal_time[3,col_ind]=difftime(ttttt_2, ttttt_1, units = c("secs")) +cal_time[3,col_ind]    }
  }
  }
  }
}
round(cal_time, 3)
```
\subsection{Task 2: Estimation Accuracy--$p$ and $k$ are small}
```{r}
# initial data
p=10
p_plus = p + 1
n_init=2*p
n_max=100
l_max=10000

set.seed(369)
otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method="regular" ,reg=4)
n_d_init=otput$n_d_init
theta=otput$theta
init_data=otput$init_data
design_X=otput$design_X
offset_b=0
k=nrow(design_X)
k0=sum(n_d_init)
#GI0/GI1/uniform/opt non-random select/opt random
  L2_Dis_Gi0_ave=rep(0,n_max-k0)
  L2_Dis_Gi1_ave=rep(0,n_max-k0)
  L2_Dis_unif_ave=rep(0,n_max-k0)
  L2_Dis_opt_D=rep(0,n_max-k0)
  L2_Dis_opt_R=rep(0,n_max-k0)
  L2_Dis_unif=rep(0,n_max-k0)
  L2_Dis_opt_ave_D=rep(0,n_max-k0)
  L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_L2_Dis_Gi0_ave=rep(0,n_max-k0)
  pi_L2_Dis_Gi1_ave=rep(0,n_max-k0)
  pi_L2_Dis_unif_ave=rep(0,n_max-k0)
  pi_L2_Dis_opt_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_R=rep(0,n_max-k0)
  pi_L2_Dis_unif=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_R=rep(0,n_max-k0)
  

  
  pi_loss_Gi0_ave=rep(0,n_max-k0)
  pi_loss_Gi1_ave=rep(0,n_max-k0)
  pi_loss_unif_ave=rep(0,n_max-k0)
  pi_loss_opt_D=rep(0,n_max-k0)
  pi_loss_opt_R=rep(0,n_max-k0)
  pi_loss_unif=rep(0,n_max-k0)
  pi_loss_opt_ave_D=rep(0,n_max-k0)
  pi_loss_opt_ave_R=rep(0,n_max-k0)
  
{
  pi_0_initial=rep(1/k,k)
  num_iter=100000
  learning_rate=0.00001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial, num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full)
}
for(kk in 1:l_max){
# opt non-random
#ot_D= adapt_opt_D_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#ot_D=oracle_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0, n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_D = L2_Dis_opt_ave_D + ot_D$L2_Dis
#pi_L2_Dis_opt_ave_D=pi_L2_Dis_opt_ave_D+ot_D$pi_L2_Dis
#pi_loss_opt_ave_D=pi_loss_opt_ave_D+ot_D$pi_loss  
  
# GI1
ot1=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi1_ave = L2_Dis_Gi1_ave + ot1$L2_Dis
pi_L2_Dis_Gi1_ave=pi_L2_Dis_Gi1_ave+ot1$pi_L2_Dis
pi_loss_Gi1_ave=pi_loss_Gi1_ave+ot1$pi_loss

# GI0
ot0=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi0_ave = L2_Dis_Gi0_ave + ot0$L2_Dis
pi_L2_Dis_Gi0_ave=pi_L2_Dis_Gi0_ave+ot0$pi_L2_Dis
pi_loss_Gi0_ave=pi_loss_Gi0_ave+ot0$pi_loss

# unif
ot_unif=adapt_unif_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
L2_Dis_unif_ave=L2_Dis_unif_ave+ot_unif$L2_Dis
pi_L2_Dis_unif_ave=pi_L2_Dis_unif_ave+ot_unif$pi_L2_Dis
pi_loss_unif_ave=pi_loss_unif_ave+ot_unif$pi_loss



# opt random select
#ot_R= adapt_opt_R_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_R = L2_Dis_opt_ave_R + ot_R$L2_Dis
#pi_L2_Dis_opt_ave_R=pi_L2_Dis_opt_ave_R+ot_R$pi_L2_Dis
#pi_loss_opt_ave_R=pi_loss_opt_ave_R+ot_R$pi_loss

}
```

```{r}
# Conversion from cm to inches
width_in_inches <- 4  
height_in_inches <- 3  

# Open a PDF device with specified dimensions
pdf("p10_oracle_MSE.pdf", width = width_in_inches, height = height_in_inches)

par(mar = c(4.2, 4.2, 1, 1))
{
  node2=(k0+1):n_max
  # Create a vector of labels for the legend
  #legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random","Opt_GI0","Opt_GI1")
  legend_labels <- c("GI0","GI1", "Unif"  )
  plot(node2, L2_Dis_Gi0_ave/l_max ,ylim = c(0, 1.1*max(L2_Dis_Gi0_ave/l_max)), 
       type = "o",  xlab = "Sample Size",ylab="MSE",
       cex=0.7, col = "grey30", lwd = 1, pch=21,cex.lab=1.5)
#  plot(node2, L2_Dis_Gi0_ave/l_max ,ylim = c(0, 1.1*max(L2_Dis_Gi0_ave/l_max)), 
#    type = "l",  xlab = "Sample Size",ylab="MSE",
#    cex=0.8, col = "grey30", lwd = 1 ,cex.lab=1.5)
  lines(node2, L2_Dis_Gi1_ave/l_max, type = "o",
        cex=0.2, col = "green",lwd = 1, lty=21, pch=19)
  lines(node2, L2_Dis_unif_ave/l_max, type = "o",
        cex=0.5, col = 4,lwd = 1, lty=4, pch=24)
#  lines(node2, L2_Dis_opt_ave_D/l_max, type = "o",
#        cex=0.2,  col = "red",lwd = 1, lty=3, pch=3)
  #  lines(node2, L2_Dis_opt_ave_R/l_max, type = "o",        cex=0.7,  col = 6, lty=5, pch=7)
  # Add a legend to the plot
  legend("topright", legend = legend_labels, 
         col = c("grey30", "green", 4 ), 
         lwd = c(1, 1, 1),
         lty = c(1, 2, 4), 
         cex = 1,
         pch = c(21,19,24), 
         bty="n")
  
}
# Close the PDF device
dev.off()
```
 
```{r}
# initial data
p=10
p_plus = p + 1
n_init=2*p
n_max=400
l_max=1000

set.seed(369)
otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method="regular" ,reg=4)
n_d_init=otput$n_d_init
theta=otput$theta
init_data=otput$init_data
design_X=otput$design_X
offset_b=0
k=nrow(design_X)
k0=sum(n_d_init)
#GI0/GI1/uniform/opt non-random select/opt random
  L2_Dis_Gi0_ave=rep(0,n_max-k0)
  L2_Dis_Gi1_ave=rep(0,n_max-k0)
  L2_Dis_unif_ave=rep(0,n_max-k0)
  L2_Dis_opt_D=rep(0,n_max-k0)
  L2_Dis_opt_R=rep(0,n_max-k0)
  L2_Dis_unif=rep(0,n_max-k0)
  L2_Dis_opt_ave_D=rep(0,n_max-k0)
  L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_L2_Dis_Gi0_ave=rep(0,n_max-k0)
  pi_L2_Dis_Gi1_ave=rep(0,n_max-k0)
  pi_L2_Dis_unif_ave=rep(0,n_max-k0)
  pi_L2_Dis_opt_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_R=rep(0,n_max-k0)
  pi_L2_Dis_unif=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_R=rep(0,n_max-k0)
  

  
  pi_loss_Gi0_ave=rep(0,n_max-k0)
  pi_loss_Gi1_ave=rep(0,n_max-k0)
  pi_loss_unif_ave=rep(0,n_max-k0)
  pi_loss_opt_D=rep(0,n_max-k0)
  pi_loss_opt_R=rep(0,n_max-k0)
  pi_loss_unif=rep(0,n_max-k0)
  pi_loss_opt_ave_D=rep(0,n_max-k0)
  pi_loss_opt_ave_R=rep(0,n_max-k0)
  
{
  pi_0_initial=rep(1/k,k)
  num_iter=100000
  learning_rate=0.00001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial, num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full)
}
for(kk in 1:l_max){
# opt non-random
#ot_D= adapt_opt_D_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#ot_D=oracle_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0, n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_D = L2_Dis_opt_ave_D + ot_D$L2_Dis
#pi_L2_Dis_opt_ave_D=pi_L2_Dis_opt_ave_D+ot_D$pi_L2_Dis
#pi_loss_opt_ave_D=pi_loss_opt_ave_D+ot_D$pi_loss  
  
# GI1
ot1=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi1_ave = L2_Dis_Gi1_ave + ot1$L2_Dis
pi_L2_Dis_Gi1_ave=pi_L2_Dis_Gi1_ave+ot1$pi_L2_Dis
pi_loss_Gi1_ave=pi_loss_Gi1_ave+ot1$pi_loss

# GI0
ot0=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi0_ave = L2_Dis_Gi0_ave + ot0$L2_Dis
pi_L2_Dis_Gi0_ave=pi_L2_Dis_Gi0_ave+ot0$pi_L2_Dis
pi_loss_Gi0_ave=pi_loss_Gi0_ave+ot0$pi_loss

# unif
ot_unif=adapt_unif_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
L2_Dis_unif_ave=L2_Dis_unif_ave+ot_unif$L2_Dis
pi_L2_Dis_unif_ave=pi_L2_Dis_unif_ave+ot_unif$pi_L2_Dis
pi_loss_unif_ave=pi_loss_unif_ave+ot_unif$pi_loss



# opt random select
#ot_R= adapt_opt_R_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_R = L2_Dis_opt_ave_R + ot_R$L2_Dis
#pi_L2_Dis_opt_ave_R=pi_L2_Dis_opt_ave_R+ot_R$pi_L2_Dis
#pi_loss_opt_ave_R=pi_loss_opt_ave_R+ot_R$pi_loss

}
``` 
 
```{r}
# Conversion from cm to inches
width_in_inches <- 4  
height_in_inches <- 3  

# Open a PDF device with specified dimensions
pdf("p10_oracle_F.pdf", width = width_in_inches, height = height_in_inches)

F_star=obj_f_full(pi_optimized)
par(mar = c(4.2, 5, 1, 1))
{
  node2=(k0+1):n_max
  # Create a vector of labels for the legend
  #legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random","Opt_GI0","Opt_GI1")
  #legend_labels <- c("GI0","GI1", "Unif", "Oracle_GI0")
  legend_labels <- c("GI0","GI1", "Unif" )

  plot(node2, pi_loss_Gi0_ave/l_max-F_star ,ylim = c(0, 1.2*max(pi_loss_Gi0_ave/l_max-F_star)), 
       type = "o",  xlab = "Sample Size",ylab=expression(F[n]),
       cex=0.7, col = "grey30", lwd = 1, pch=21,cex.lab=1.5)
  lines(node2, pi_loss_Gi1_ave/l_max-F_star, type = "o",
        cex=0.2, col = "green",lwd = 1, lty=2, pch=19)
  lines(node2, pi_loss_unif_ave/l_max-F_star, type = "o",
        cex=0.3, col = 4,lwd = 1, lty=4, pch=24)
#  lines(node2, pi_loss_opt_ave_D/l_max-F_star, type = "o",
#        cex=0.2,  col = "red",lwd = 1, lty=3, pch=3)
 # lines(node2, pi_loss_opt_ave_R/l_max, type = "o",
#        cex=0.7,  col = 6, lty=5, pch=7)
  # Add a legend to the plot
  legend("topright", legend = legend_labels, 
         col = c("grey30", "green", 4 ), 
         lwd = c(1, 1, 1),
         lty = c(1, 2, 4), 
         cex = 1,
         pch = c(21,19, 24), 
         bty="n")

}
# Close the PDF device
dev.off()
```

\subsection{Task 3: Estimation Accuracy--$p$ and $k$ are large}
```{r}
# initial data
p=50
p_plus = p + 1
n_init=2*p
n_max=200
l_max=10000

set.seed(6)
otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method="regular" ,reg=4)
n_d_init=otput$n_d_init
theta=otput$theta
init_data=otput$init_data
design_X=otput$design_X
offset_b=0
k=nrow(design_X)
k0=sum(n_d_init)
#GI0/GI1/uniform/opt non-random select/opt random
  L2_Dis_Gi0_ave=rep(0,n_max-k0)
  L2_Dis_Gi1_ave=rep(0,n_max-k0)
  L2_Dis_unif_ave=rep(0,n_max-k0)
  L2_Dis_opt_D=rep(0,n_max-k0)
  L2_Dis_opt_R=rep(0,n_max-k0)
  L2_Dis_unif=rep(0,n_max-k0)
  L2_Dis_opt_ave_D=rep(0,n_max-k0)
  L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_L2_Dis_Gi0_ave=rep(0,n_max-k0)
  pi_L2_Dis_Gi1_ave=rep(0,n_max-k0)
  pi_L2_Dis_unif_ave=rep(0,n_max-k0)
  pi_L2_Dis_opt_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_R=rep(0,n_max-k0)
  pi_L2_Dis_unif=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_loss_Gi0_ave=rep(0,n_max-k0)
  pi_loss_Gi1_ave=rep(0,n_max-k0)
  pi_loss_unif_ave=rep(0,n_max-k0)
  pi_loss_opt_D=rep(0,n_max-k0)
  pi_loss_opt_R=rep(0,n_max-k0)
  pi_loss_unif=rep(0,n_max-k0)
  pi_loss_opt_ave_D=rep(0,n_max-k0)
  pi_loss_opt_ave_R=rep(0,n_max-k0)
  
{
  pi_0_initial=rep(1/k,k)
  num_iter=100000000
  learning_rate=0.0000001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial, num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full, tol = 1e-12)
  }
  
for(kk in 1:l_max){

# GI1
ot1=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi1_ave = L2_Dis_Gi1_ave + ot1$L2_Dis
pi_L2_Dis_Gi1_ave=pi_L2_Dis_Gi1_ave+ot1$pi_L2_Dis
pi_loss_Gi1_ave=pi_loss_Gi1_ave+ot1$pi_loss

# GI0
ot0=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi0_ave = L2_Dis_Gi0_ave + ot0$L2_Dis
pi_L2_Dis_Gi0_ave=pi_L2_Dis_Gi0_ave+ot0$pi_L2_Dis
pi_loss_Gi0_ave=pi_loss_Gi0_ave+ot0$pi_loss

# unif
ot_unif=adapt_unif_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
L2_Dis_unif_ave=L2_Dis_unif_ave+ot_unif$L2_Dis
pi_L2_Dis_unif_ave=pi_L2_Dis_unif_ave+ot_unif$pi_L2_Dis
pi_loss_unif_ave=pi_loss_unif_ave+ot_unif$pi_loss

# opt non-random
#ot_D=oracle_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0, n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_D = L2_Dis_opt_ave_D + ot_D$L2_Dis
#pi_L2_Dis_opt_ave_D=pi_L2_Dis_opt_ave_D+ot_D$pi_L2_Dis
#pi_loss_opt_ave_D=pi_loss_opt_ave_D+ot_D$pi_loss


# opt random select
#ot_R= adapt_opt_R_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_R = L2_Dis_opt_ave_R + ot_R$L2_Dis
#pi_L2_Dis_opt_ave_R=pi_L2_Dis_opt_ave_R+ot_R$pi_L2_Dis
#pi_loss_opt_ave_R=pi_loss_opt_ave_R+ot_R$pi_loss

}
```

```{r}
# Conversion from cm to inches
width_in_inches <- 4  
height_in_inches <- 3  

# Open a PDF device with specified dimensions
pdf("p50_oracle_MSE.pdf", width = width_in_inches, height = height_in_inches)

par(mar = c(4.2, 4.2, 1, 1))
{
  node2=(k0+1):n_max
  # Create a vector of labels for the legend
  #legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random","Opt_GI0","Opt_GI1")
  #legend_labels <- c("GI0","GI1", "Unif", "Oracle_GI0" )
  legend_labels <- c("GI0","GI1", "Unif" )

  plot(node2, L2_Dis_Gi0_ave/l_max ,ylim = c(0.8*min(L2_Dis_opt_ave_D/l_max), 1.1*max(L2_Dis_Gi0_ave/l_max)), 
       type = "o",  xlab = "Sample Size",ylab="MSE",
       cex=0.5, col = "grey30", lwd = 1, pch=21,cex.lab=1.5)
#  plot(node2, L2_Dis_Gi0_ave/l_max ,ylim = c(0, 1.1*max(L2_Dis_Gi0_ave/l_max)), 
#    type = "l",  xlab = "Sample Size",ylab="MSE",
#    cex=0.8, col = "grey30", lwd = 1 ,cex.lab=1.5)
  lines(node2, L2_Dis_Gi1_ave/l_max, type = "o",
        cex=0.2, col = "green",lwd = 1, lty=21, pch=19)
  lines(node2, L2_Dis_unif_ave/l_max, type = "o",
        cex=0.3, col = 4,lwd = 1, lty=4, pch=24)
#  lines(node2, L2_Dis_opt_ave_D/l_max, type = "o",
#        cex=0.3,  col = "red",lwd = 1, lty=3, pch=3)
  #  lines(node2, L2_Dis_opt_ave_R/l_max, type = "o",        cex=0.7,  col = 6, lty=5, pch=7)
  # Add a legend to the plot
  legend("topright", legend = legend_labels, 
         col = c("grey30", "green", 4 ), 
         lwd = c(1, 1, 1),
         lty = c(1, 2, 4), 
         cex = 1,
         pch = c(21,19, 24), 
         bty="n")
  
}
# Close the PDF device
dev.off()
```

```{r}
# initial data
p=50
p_plus = p + 1
n_init=2*p
n_max=400
l_max=1000

set.seed(6)
otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method="regular" ,reg=4)
n_d_init=otput$n_d_init
theta=otput$theta
init_data=otput$init_data
design_X=otput$design_X
offset_b=0
k=nrow(design_X)
k0=sum(n_d_init)
#GI0/GI1/uniform/opt non-random select/opt random
  L2_Dis_Gi0_ave=rep(0,n_max-k0)
  L2_Dis_Gi1_ave=rep(0,n_max-k0)
  L2_Dis_unif_ave=rep(0,n_max-k0)
  L2_Dis_opt_D=rep(0,n_max-k0)
  L2_Dis_opt_R=rep(0,n_max-k0)
  L2_Dis_unif=rep(0,n_max-k0)
  L2_Dis_opt_ave_D=rep(0,n_max-k0)
  L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_L2_Dis_Gi0_ave=rep(0,n_max-k0)
  pi_L2_Dis_Gi1_ave=rep(0,n_max-k0)
  pi_L2_Dis_unif_ave=rep(0,n_max-k0)
  pi_L2_Dis_opt_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_R=rep(0,n_max-k0)
  pi_L2_Dis_unif=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_D=rep(0,n_max-k0)
  pi_L2_Dis_opt_ave_R=rep(0,n_max-k0)
  
  pi_loss_Gi0_ave=rep(0,n_max-k0)
  pi_loss_Gi1_ave=rep(0,n_max-k0)
  pi_loss_unif_ave=rep(0,n_max-k0)
  pi_loss_opt_D=rep(0,n_max-k0)
  pi_loss_opt_R=rep(0,n_max-k0)
  pi_loss_unif=rep(0,n_max-k0)
  pi_loss_opt_ave_D=rep(0,n_max-k0)
  pi_loss_opt_ave_R=rep(0,n_max-k0)
  
{
  pi_0_initial=rep(1/k,k)
  num_iter=100000000
  learning_rate=0.0000001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial, num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full, tol = 1e-12)
  }
  
for(kk in 1:l_max){

# GI1
ot1=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi1_ave = L2_Dis_Gi1_ave + ot1$L2_Dis
pi_L2_Dis_Gi1_ave=pi_L2_Dis_Gi1_ave+ot1$pi_L2_Dis
pi_loss_Gi1_ave=pi_loss_Gi1_ave+ot1$pi_loss

# GI0
ot0=adapt_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0 , n_max = n_max , pi_optimized, n_d_init)
L2_Dis_Gi0_ave = L2_Dis_Gi0_ave + ot0$L2_Dis
pi_L2_Dis_Gi0_ave=pi_L2_Dis_Gi0_ave+ot0$pi_L2_Dis
pi_loss_Gi0_ave=pi_loss_Gi0_ave+ot0$pi_loss

# unif
ot_unif=adapt_unif_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
L2_Dis_unif_ave=L2_Dis_unif_ave+ot_unif$L2_Dis
pi_L2_Dis_unif_ave=pi_L2_Dis_unif_ave+ot_unif$pi_L2_Dis
pi_loss_unif_ave=pi_loss_unif_ave+ot_unif$pi_loss

# opt non-random
#ot_D=oracle_seq_tr_glmnet_RA( design_X, init_data,  method.order = 0, n_max = n_max , pi_optimized, #n_d_init, box_R=3)
#L2_Dis_opt_ave_D = L2_Dis_opt_ave_D + ot_D$L2_Dis
#pi_L2_Dis_opt_ave_D=pi_L2_Dis_opt_ave_D+ot_D$pi_L2_Dis
#pi_loss_opt_ave_D=pi_loss_opt_ave_D+ot_D$pi_loss


# opt random select
#ot_R= adapt_opt_R_glmnet_RA( design_X, init_data,  n_max = n_max , pi_optimized, n_d_init, box_R=3)
#L2_Dis_opt_ave_R = L2_Dis_opt_ave_R + ot_R$L2_Dis
#pi_L2_Dis_opt_ave_R=pi_L2_Dis_opt_ave_R+ot_R$pi_L2_Dis
#pi_loss_opt_ave_R=pi_loss_opt_ave_R+ot_R$pi_loss

}
```
 
```{r}
# Conversion from cm to inches
width_in_inches <- 4  
height_in_inches <- 3  

# Open a PDF device with specified dimensions
pdf("p50_oracle_F.pdf", width = width_in_inches, height = height_in_inches)

F_star=obj_f_full(pi_optimized)
par(mar = c(4.2, 5, 1, 1))
{
  node2=(k0+1):n_max
  # Create a vector of labels for the legend
  #legend_labels <- c("GI0","GI1", "Unif", "Opt_deterministic", "Opt_random","Opt_GI0","Opt_GI1")
  #legend_labels <- c("GI0","GI1", "Unif", "Oracle_GI0")
  legend_labels <- c("GI0","GI1", "Unif" )
  plot(node2, pi_loss_Gi0_ave/l_max-F_star ,ylim = c(0, 1.2*max(pi_loss_Gi0_ave/l_max-F_star)), 
       type = "o",  xlab = "Sample Size",ylab=expression(F[n]),
       cex=0.7, col = "grey30", lwd = 1, pch=21,cex.lab=1.5)
  lines(node2, pi_loss_Gi1_ave/l_max-F_star, type = "o",
        cex=0.2, col = "green",lwd = 1, lty=2, pch=19)
  lines(node2, pi_loss_unif_ave/l_max-F_star, type = "o",
        cex=0.5, col = 4,lwd = 1, lty=4, pch=24)
#  lines(node2, pi_loss_opt_ave_D/l_max-F_star, type = "o",
#        cex=0.2,  col = "red",lwd = 1, lty=3, pch=3)
 # lines(node2, pi_loss_opt_ave_R/l_max, type = "o",
#        cex=0.7,  col = 6, lty=5, pch=7)
  # Add a legend to the plot
  legend("topright", legend = legend_labels, 
         col = c("grey30", "green", 4 ), 
         lwd = c(1, 1, 1 ),
         lty = c(1, 2, 4 ), 
         cex = 1,
         pch = c(21,19, 24 ), 
         bty="n")

}
# Close the PDF device
dev.off()
``` 
\subsection{Task 4: Impact of the side length of compact set $\Theta$}
```{r}
# initial data
p=50
p_plus = p + 1
n_init=p
n_max=2000
l_max=100

set.seed(777)
otput=init_edge_generate_RA(p_plus=p_plus, n_init=n_init, method="regular")
n_d_init=otput$n_d_init
theta=otput$theta
init_data=otput$init_data
design_X=otput$design_X
edges=otput$pair_matrix
offset_b=0
k=nrow(design_X)
k0=sum(n_d_init)

# GI1 
kendall_1=rep(0,n_max-k0)
kendall_2=rep(0,n_max-k0)
kendall_3=rep(0,n_max-k0)
kendall_4=rep(0,n_max-k0)

{
  pi_0_initial=rep(1/k,k)
  num_iter=100000000
  learning_rate=0.0000001
  # using gradient descent to solve opt proportion
  pi_optimized <- projected_gradient_descent(pi_0_initial, num_iters=num_iter, learning_rate=learning_rate,  grad_obj=grad_f_full, tol = 1e-12)
}

for(kk in 1:l_max){
  # GI1
  ot1=adapt_seq_tr_glmnet_RA_kendall( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init,box_R=1)
  kendall_1 = kendall_1 + ot1$kendall
  
  # GI1
  ot2=adapt_seq_tr_glmnet_RA_kendall( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init,box_R=2)
  kendall_2 = kendall_2 + ot2$kendall
  
  # GI1
  ot3=adapt_seq_tr_glmnet_RA_kendall( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init,box_R=3)
  kendall_3 = kendall_3 + ot3$kendall
  
  # GI1
  ot4=adapt_seq_tr_glmnet_RA_kendall( design_X, init_data,  method.order = 1 , n_max = n_max , pi_optimized, n_d_init,box_R=5)
  kendall_4 = kendall_4 + ot4$kendall

}
```

```{r}
par(mar = c(4.2, 4.2, 1, 1)) 
{
  node2 <- (k0+1):n_max
  legend_labels <- c("cube1", "cube2", "cube3", "cube5")
  plot(node2, kendall_1/l_max, ylim = c(0.2, 1), 
       type = "l", xlab = "Sample Size", ylab = "Kendall's Correlation",
       cex = 1, col = "grey30", lwd = 2, cex.lab=1.5)  # Increase lwd here for a bolder line
  
  lines(node2, kendall_2/l_max, type = "l",
        cex = 1, col = 4, lwd = 2, lty = 4)  # Increase lwd here
  
  lines(node2, kendall_3/l_max, type = "l",
        cex = 1, col = "red", lwd = 2, lty = 3)  # Increase lwd here
  
  lines(node2, kendall_4/l_max, type = "l",
        cex = 1, col = 6, lty = 5, lwd = 2)  # Increase lwd here
  
  
  legend("bottomright", legend = legend_labels, 
         col = c("grey30", 4, "red", 6), 
         lwd = c(2, 2, 2, 2),  # Increase lwd in legend
         lty = c(1, 4, 3, 5), 
         cex = 1.5,  # Increase cex for a bigger text in the legend
         bty = "n")
}

```
